SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-22 paper.tex
review 4. RESEARCH PROBLEM (RP)

\textbf{(RP1)} providing suitable encoding into the Satisfiability Modulo Theories (SMT) \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.

\textbf{(RP2)} exploiting SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving.

\textbf{(RP3)} proving correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware.

\textbf{(RP4)} incorporating knowledge about system purpose and associated features, which aims to detect system-level and behavior failures.

>>>>

\textbf{(RP1)} provide suitable encoding into the Satisfiability Modulo Theories (SMT) \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.

\textbf{(RP2)} exploit SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving.

\textbf{(RP3)} prove correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware.

\textbf{(RP4)} incorporate knowledge about system purpose and associated features, which aims to detect system-level and behavior failures.
